### 2022-11-17 chapter1/chapter1.tex
Wrapped code availability in sloppypar to prevent overfull lines

\subsection*{Code and data availability}
The code used to produce the results and analyses is available at \url{https://github.com/marcsingleton/orthology_inference2023}. HMM algorithms were implemented in the standalone package Homomorph which is available at \url{https://github.com/marcsingleton/homomorph} and on the Python Package Index (PyPI). The following Python libraries were used: matplotlib, NumPy, pandas, SciPy, and TensorFlow~\cite{Hunter2007, Harris2020, McKinney2010, Virtanen2020, Abadi2015}. Relevant output files are available in the supporting information. There is no primary data associated with this manuscript. All primary data are available from publicly accessible sources described in their corresponding sections.

>>>>

\subsection*{Code and data availability}
\begin{sloppypar}
The code used to produce the results and analyses is available at \url{https://github.com/marcsingleton/orthology_inference2023}. HMM algorithms were implemented in the standalone package Homomorph which is available at \url{https://github.com/marcsingleton/homomorph} and on the Python Package Index (PyPI). The following Python libraries were used: matplotlib, NumPy, pandas, SciPy, and TensorFlow~\cite{Hunter2007, Harris2020, McKinney2010, Virtanen2020, Abadi2015}. Relevant output files are available in the supporting information. There is no primary data associated with this manuscript. All primary data are available from publicly accessible sources described in their corresponding sections.
\end{sloppypar}
